
---
title: "Data Collection for NASA NEOs Corsework"
author: "Surya Ramesh"
date: "12/02/2021"
output:
  pdf_document:
    toc: yes
    number_sections: yes
  html_document:
    toc: yes
    df_print: paged
---   


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include = FALSE}

library(httr)
library(jsonlite)
library(dplyr)
library(rlist)
library(codebook)#remove
```

## Get data from API

  
  - assemble the url with start and end dates as modifiable.
  - check for any http error and set error message in case it does
  - Save the JSON content of response  as text for readability 
  - Format the content - flatten, stack the data frame inside and merge with content,remove the original data frame
  - Write to CSV for sharing
  
  

```{r}

# modify the start_daterange and end_daterange to the dates required
#smaller range shown here

start_daterange <- as.Date("2021-02-12", "%Y-%m-%d") 
end_daterange <- as.Date("2021-02-18", "%Y-%m-%d")

date <- start_daterange

MycombinedData <- data.frame() # empty dataframe for the data

# Loop to get data from API and format it. 

while (date <= end_daterange)
  
{
  url <- paste(
    "https://api.nasa.gov/neo/rest/v1/feed?start_date=",
    format(date, "%Y-%m-%d"),"&end_date=",format(date + 7, "%Y-%m-%d"),
    "&detailed=true&api_key=N0spzeNK1l22GJ1u8mAKqm0XHDE5dAbhhGvWRrFo",
    sep = "",collapse = NULL)
  
  
  #print(url)                               # for troubleshooting
  
  response <- GET(url)                      # the GET command for API 
  
  #Check for http error response from API 
  
  if (http_error(response))
  {
    
    stop("The API request failed")
  }
  
  # Return the response's content which contains the data needed
  
  #content(response)                       # for troubleshooting
  
  
  # Parse returned content as text
  
  my_json <- content(response, as = 'text')
  
  
  #write to individual JSON files for sharing
  
  write(my_json, paste(format(date, "%Y-%m-%d"), "_NASANeoWS.json"))
  
  # Format the data 
  
  my_json_flat <- fromJSON(my_json, flatten = TRUE)
  
  NEOs <- my_json_flat$near_earth_objects
  
  NEOs_list <- list.stack(NEOs)
  
  close_approach_data_list <-list.stack(NEOs_list$close_approach_data)
  
  #merge NEOs_list list and flattened close_approach_data_list
  
  merged_df_original <-data.frame(NEOs_list, close_approach_data_list)
  
  #remove original close_approach_data column
  
  merged_df_original$close_approach_data <- NULL
  
  # print(nrow(merged_df_original)) # used for troubleshooting
  
  # bind the rows to MycombinedData
  
  MycombinedData <- rbind(MycombinedData, merged_df_original) 
  
  
  date <- date + 7
  
  #Sys.sleep(120)     # sys sleeps for 120secs to avoid too many requests
}

```

## Write to CSV file 
```{r}


write.csv(MycombinedData , "MyNASAData.csv")

#nrow(MycombinedData)  # used for troubleshooting
#View(MycombinedData)  # used for troubleshooting

```


End of Data Collection section
